---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# cidata

cidata is a data package for R that includes 4 data sets used in Causal Inference by Hernán and Robins: `nhefs`, a cleaned version of NHEFS data, `nhefs_complete`, a complete case version of `nhefs`, `nhefs_codebook`, the codebook for NHEFS, and `greek_data`, the data from Table 2.2 used in Chapter 13.

## Installation

You can install cidata from GitHub with:

``` r
remotes::install_github("malcolmbarrett/cidata") 
```

## Example

cidata loads a cleaned version of the NHEFS data used in Causal Inference, `nhefs`. There is also a complete case version, `nhefs_complete`, and a codebook for the variables in NHEFS, `nhefs_codebook`.

```{r nhefs}
library(cidata)
nhefs
```

cidata also loads the data in Table 2.2 of Causal Inference, which is used as an example in Chapter 13.

```{r greek}
greek_data
```
